Replicating Blair and Sambanis: Forecasting Civil Wars - JCR 2020

### 2020-04-29 issues.Rmd

- Their train/test approach 
  - 5-year forecasts for sep plots and AUC scores)
- Lack of yearly test forecasts in favor of a single 5-year test forecast
- The lack of procedures to account for rare events in an RF model

>>>>

- Their train/test approach 
  - 5-year forecasts for sep plots and AUC scores)
- Smoothing of AUC/ROC scores
- Lack of yearly test forecasts in favor of a single 5-year test forecast
- The lack of procedures to account for rare events in an RF model
